%\providecommand{\main}{../../main}
\documentclass[../../main]{subfiles}

\newendnotes{d}
\input{ch4notes.txt}
%\setcounter{dnote}{\value{cnote}}
\setcounter{dnote}{\value{anote}}
% \newcommand{\Dnote}[1]{\dnote{#1}\big)}
\newcommand{\Dnote}[1]{\dnote{#1}}

\begin{document}

This is the first chapter constituting the novel results of this work. Here
balancedly splittable orthogonal designs are defined and various constructions
are presented. These most interesting objects are connected to several objects
such as frames and pairs of unbiased orthogonal designs. Aside from \S 5, the
results presented here are shown in \cite{split-od}.

\fancyhf{}

\fancyhead[RO,LE]{\thepage}
% \fancyfoot[C]{\thepage}
\fancyhead[CO]{\S\thesection. Balancedly Splittable Hadamard Matrices}
\fancyhead[CE]{Chapter \thechapter. Balancedly Splittable Orthogonal Designs}

 \section{\centering Balancedly Splittable Hadamard Matrices}
 The results of this section are due to \cite{splittable-hadamard}. We include
 this material here to evince the fact that the concept of a balancedly
 splittable orthogonal design is a generalization of previous work and to
 provide a more intuitive introduction to the concept. 
 
 \dinkus
 
 \subfile{./bhadamard/bhadamard}
 
 \fancyhf{}

 \fancyhead[RO,LE]{\thepage}
 % \fancyfoot[C]{\thepage}
 \fancyhead[CO]{\S\thesection. Balancedly Splittable Orthogonal Designs}
 \fancyhead[CE]{Chapter \thechapter. Balancedly Splittable Orthogonal Designs}
 
 \section{\centering Balancedly Splittable Orthogonal Designs}
 In this and the following section, the new results of \cite{split-od} are
 presented. Here we define balanced splittability of orthogonal designs and give
 several constructions. To avoid obfuscation, we given the constructions in
 terms of real and complex ODs; however, the results are perfectly valid for the
 more general QODs. 
 
 \dinkus
 
 \subfile{./bod/bod}
 
 \fancyhf{}

 \fancyhead[RO,LE]{\thepage}
 % \fancyfoot[C]{\thepage}
 \fancyhead[CO]{\S\thesection. Related Configurations}
 \fancyhead[CE]{Chapter \thechapter. Balancedly Splittable Orthogonal Designs}

 \section{\centering Related Configurations}
 In this section, the balancedly splittable orthogonal designs of the previous
 section are applied in the construction of related objects. We will explore
 quasi-symmetric balanced incomplete block designs, equiangular tight frames,
 and unbiased orthogonal designs. 
 
 \dinkus
 
 \subfile{./frames/frames}
 
 \singlespace
 
 \fancyhf{}

 \fancyhead[RO,LE]{\thepage}
 % \fancyfoot[C]{\thepage}
 \fancyhead[CO]{Notes}
 \fancyhead[CE]{Chapter \thechapter. Balancedly Splittable Orthogonal Designs}

 \addcontentsline{toc}{section}{Notes}
 \section*{\centering Notes}
 \thednotes
 
 \doublespacing
 
 \biblio
\end{document}
