\documentclass[../../main]{subfiles}

\begin{document}
 
 \begin{longtabu} to \textwidth{X[1,l] X[2,l]} %[c]{l p{3.5in}}
 $\N$ & The additive semigroup of natural numbers $\{0,1,2\dots$\}. \\
 $\Z$ & The ring of integers $\{0, \pm1, \pm2, \dots$\}. \\
 $\Q$ & The rational number field $\{\frac{n}{m} : n,m \in \Z\}$. \\
 $\R$ & The real number field. \\
 $\C$ & The complex number field $\{x+y\sqrt{-1} : x,y \in \R\}$. \\
 $\Z/n\Z$ & The integers modulo $n$ $\{\overline{0}, \dots, \overline{n-1}\}$. \\
 $\gf(q)$ & The Galois field of $q$ elements. \\
 $\D=(X,\B)$ & A balanced incomplete block design with point set $X$ and block set $\B$. \\
 $\bibd(v,k,\lambda)$ & A balanced incomplete block design with associated parameters. \\
 $\comp(\D)$ & Complementary design of $\D$. \\
 $\res(\D)$ & Residual design of $\D$. \\
 $\der(\D)$ & Derived design of $\D$. \\
 $A(\D)$ & Incidence matrix of the design $\D$. \\
 $\gdd(m,n,k,\lambda_1,\lambda_2)$ & A group divisible design with associated parameters. \\
 $\ds(v,k,\lambda)$ & A difference set of size $k$ on a group of order $v$ with index $\lambda$. \\
 $\dev(D)$ & The development of the set $D$. \\
 D$(m,q)$ & Singer difference set. \\
 $\rds(m,n,k,\lambda)$ & A relative difference set of size $k$, on a group of order $mn$, with index $\lambda$, and relative to a normal subgroup of order $n$. \\
 P$(m,q)$ & The projective space of dimension $m$. \\
 $[n,k,d,w]_q$-code & A linear code in $\gf(q^n)$ of dimension $k$, minimum distance $d$, and minimum weight $w$. \\
 $(n,M,d,w)_q$-code & A nonlinear code in an alphabet of $q$ letters of length $n$, with $M$ codewords, minimum distance $d$, and minimum weight $w$. \\
 $\M_q(n,d,w)$ & The maximum size of any $(n,M,d,w)_q$-code, i.e. $M \leq \M_q(n,d,w)$. \\
 $\w(v,k)$ & A weighing matrix of order $v$ and weight $k$. \\
 $\bw(v,k;n)$ & A Butson weighing matrix of order $v$ and weight $k$ over the $n$-th roots of unity. \\
 $\gw(v,k;G)$ & A generalized weighing matrix of order $v$ and weight $k$ over the finite group $G$. \\
 $\gbrd(v,k,\lambda;G)$ & A generalized Bhaskar Rao design over the finite group $G$ with associated parameters. \\
 $\bgw(v,k,\lambda;G)$ & A balanced generalized weighing matrix of order $v$, weight $k$, and index $\lambda/|G|$, over the finite group $G$. \\
 $\srg(v,k,\lambda,\mu)$ & A strongly regular graph with associated parameters. \\
 $A(\Gamma)$ & The adjacency matrix of the graph $\Gamma$. \\
 $\X=(X,\RR)$ & An association scheme with point set $X$ and relations $\RR$. \\
 $\tau(A)$ & The sum of the elements of the matrix $A$. \\
 $\tr(A)$ & The sum of the diagonal elements of the matrix $A$. \\
 $\simplex_{q,n}$ & A generalized simplex code. \\
 $\hamming_{q,n}$ & A generalized Hamming code. \\
 $A \otimes B$ & The Kronecker product of $A$ by $B$.
 \end{longtabu}

\end{document}
